---
title: "Civet occurrence in Taiwan"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Paguma larvata is the scientific name of the Masked palm civet, which lives throughout Taiwan. We import the occurrence data (Human observation) available at the Global Biodiversity Information Facility (https://www.gbif.org/) using the rgbif package.

```{r,  eval=T}
library(rgbif)
library(maps)
library(sf)
library(geodata)
library(ggplot2)
library(ggspatial)
library(leaflet)
library(dplyr)
```


```{r}
gbif_civet<-occ_search(scientificName="Paguma larvata", hasCoordinate=T, basisOfRecord='HUMAN_OBSERVATION', limit=1000)
gbif_civet<-gbif_civet$data
```
Check the datum is WGS84

```{r}
str(gbif_civet)
```

It seems it is but just in case we transform the data set to an sf object so we can make sure the map and the points share the same projection.

```{r}
civet_sf <- st_as_sf(gbif_civet, coords = c("decimalLongitude", "decimalLatitude"), crs = 4326)
```

Now we can transform CRS to EPSG:4326

```{r}
civet_sf <- st_transform(civet_sf, crs = 4326)
```

And we check the projection of the civet_sf object:

```{r}
st_crs(civet_sf)
```


Then we map the occurrence data.
```{r}
maps::map('world',xlim=c(119,123), ylim=c(21,26))
points(gbif_civet$decimalLongitude, gbif_civet$decimalLatitude, col='blue',  pch=19)
```


Filter out the points that are outside of the territory of Taiwan:
```{r}
civet_sf <- civet_sf %>%
  filter(st_coordinates(.)[, 1] >= 119 & st_coordinates(.)[, 1] <= 122.5 &
         st_coordinates(.)[, 2] >= 21.5 & st_coordinates(.)[, 2] <= 25.5)
```



Or do an interactive map

```{r}
leaflet(data = civet_sf) %>%
  addProviderTiles("CartoDB.Positron") %>%  
  addCircleMarkers(
    ~st_coordinates(geometry)[, 1], ~st_coordinates(geometry)[, 2],  
    radius = 4,
    color = "blue",
    fillOpacity = 0.7,
    popup = ~paste("Location:", name)  
  ) %>%
  setView(lng = 121, lat = 23.5, zoom = 7)  
```

